\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{url}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{helvet}

% Set default font to Helvetica (sans-serif)
\renewcommand{\familydefault}{\sfdefault}

% Remove page numbering
\pagestyle{empty}

% Define colors
\definecolor{mediumgray}{RGB}{102,102,102}
\definecolor{lightgray}{RGB}{128,128,128}

% Customize section formatting
\titleformat{\section}
  {\Large\bfseries}
  {\thesection}{0em}{}
\renewcommand{\titlerule}{\color{black}\hrule width\textwidth height 0.8pt}
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Customize subsection formatting
\titleformat{\subsection}
  {\large\bfseries}
  {\thesubsection}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

% Custom command for job titles/positions
\newcommand{\jobtitle}[1]{\textbf{\color{mediumgray}#1}}
\newcommand{\institution}[1]{\textit{#1}}
\newcommand{\daterange}[1]{\textcolor{lightgray}{#1}}

% Remove list indentation and customize
\setlist[itemize]{leftmargin=0pt, itemsep=2pt, parsep=0pt}

% Custom header environment
\newenvironment{cvheader}
{\begin{center}\Large}
{\end{center}}

% Custom contact info environment
\newenvironment{contactinfo}
{\small\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}}
{\end{tabular*}}

\begin{document}

%% Header with name
\begin{cvheader}
{\Huge\textbf{Cover Letter}}\\
{\large\textcolor{mediumgray}{J. Kenneth Jung}}
\end{cvheader}

\vspace{8pt}

Dear Hiring Committee,

I write to apply for the Assistant Professor position at the Department of Resource Economics and Environmental Sociology at the University of Alberta. As a practitioner of industrial organization tools applied to questions in resource economics during my PhD candidacy at Yale University, I am excited at the prospect of advancing my research agenda at an interdisciplinary department like REES. I further hope to meaningfully contribute to the broader academic community at the University of Alberta and foster interdepartmental collaboration.

My research demonstrates how methods from industrial organization can illuminate environmental policy questions involving strategic interactions. My job market paper examines timber auctions designed to control the mountain pine beetle outbreak using structural methods to model the behavior of logging firms and measure policy counterfactuals. Similarly, my work on fishery buybacks identifies novel channels through which license retirement programs affect market outcomes, employing structural modeling to evaluate alternative policy designs. This approach allows me to address fundamental resource management challenges while making methodological insights relevant to both social and physical scientists.

In a similar vein, my teaching philosophy emphasizes inclusive, responsive pedagogy that removes barriers to student success. As a Teaching Fellow across environmental economics, econometrics, and other courses, I have redesigned course structures to improve accessibility—transforming office hours, creating peer learning environments, and developing clear materials with real-world examples. I work individually with students facing diverse challenges while building supportive learning communities through collaborative discussions and structured peer interaction.

As an active participant of both the Department of Economics and the School of the Environment at Yale University, I believe that my interdisciplinary orientation aligns with your department's mission. I describe my background and philosophy toward research and pedagogy in further detail in the enclosed materials. I am excited for the potential opportunity to contribute to the University of Alberta's research community and inclusive education mission.

Thank you for your consideration.

Sincerely,

Ken Jung

\end{document}